ERSPAN Support for Linux

### 2018-10-15 paper.tex
finish section 3

\section{Example Use Case}
\begin{figure}
{\scriptsize
\begin{verbatim}
 session 10            Linux, session 20        Linux, session 30
+----------+         +-------------------+      +----------------+
| Physical |         |     VM1  VM2 ...  |      |     linux      |
| Machines |         | 10.1.1.3  |       |      |    netdevs     |
+----------+         |  +--------------+ |      |      |         |
    | links          |  | Open vSwitch | |      | ERSPAN 10.1.1.4|
    | 10.1.1.2       |  +--------------+ |      | netdev         |
+------------+       +-------||----------+      +-||------------+ 
|Cisco switch|               ||                   ||
+------------+               || ERSPAN            || ERSPAN
   || ERSPAN tunnel          || tunnel            || tunnel
   || (192.168.1.2)          || (192.168.1.3)     || (192.168.1.4)
    /~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\     +-------+ 
    {       Layer 3 IPv4, Ipv6 network             } === |Traffic|
    \~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~/     |Sniffer|
                192.168.1.*                              +-------+
                                                        192.168.1.1
\end{verbatim}   
}
\vspace{-0.5em}
\caption{Example of creating three ERSPAN monitoring sessions, $10, 20, 30$,
in a $10.1.1.*$ internal network, mirroring traffic over a $192.168.1.*$ IP network.}
\label{example}
\vspace{-1.0em}
\end{figure}

@@

# flow entry for port 2 to erspan tunnel 
ovs-dpctl add-flow \
    "in_port(2)" \  // any packets matching in_port=2
    "set(tunnel(tun_id=20,dst=192.168.1.1,ttl=64,\
    erspan(ver=2,dir=1,hwid=0x4),flags(df|key))),3"
\end{verbatim}

%\begin{lstlisting}[caption={Example ovs-dpctl usage},language=bash,label=lst:dpctl,breaklines=true]
%\end{lstlisting}

\subsection{eBPF and iproute2}\label{iproute2}

Assuming we want to make a copy of all traffic from the physical
device eth1, and encapsulate them through ERSPAN tunnel.
We first create a native-mode ERSPAN tunnel using ip-link command,
and make a copy of all traffic from eth1 to the ERSPAN tunnel netdev.
%see net/ip6_gre_headroom.sh
\begin{verbatim}
ip link add dev myerspan type erspan seq key 30 \
    local 192.168.1.4 remote 192.168.1.1 \
    erspan_ver 1 erspan 123
tc filter add dev eth1 ingress pref 1000 matchall skip_hw \
    action mirred egress mirror dev myerspan
\end{verbatim}

For the eBPF tunnel cases,
we create a metadata mode erspan tunnel, and set the
remote ip and tunnel id to 30, attach the eBPF program,
and create the fowarding rule using tc.
\begin{verbatim}
ip link add dev myerspan type erspan external
tc qdisc add dev myerspan clsact
tc filter add dev myerspan bpf da obj test_tunnel_kern.o section set_erspan
tc filter add dev eth1 ingress pref 1000 matchall skip_hw \
    action mirred egress mirror dev myerspan
\end{verbatim}

\section{Conclusion}
\section{Future Work}
\section{Acknowledgments}

\bibliography{paper.bib}
\bibliographystyle{plain}

>>>>

\section{Example Use Case}
\begin{figure}
{\scriptsize
\begin{verbatim}
 session 10            Linux, session 20        Linux, session 30
+----------+         +-------------------+      +----------------+
| Physical |         |     VM1  VM2 ...  |      |     linux      |
| Machines |         | 10.1.1.3  |       |      |   netdev,eth1  |
+----------+         |  +--------------+ |      |      |         |
    | links          |  | Open vSwitch | |      | ERSPAN 10.1.1.4|
    | 10.1.1.2       |  +--------------+ |      | netdev         |
+------------+       +-------||----------+      +-||------------+ 
|Cisco switch|               ||                   ||
+------------+               || ERSPAN            || ERSPAN
   || ERSPAN tunnel          || tunnel            || tunnel
   || (192.168.1.2)          || (192.168.1.3)     || (192.168.1.4)
    /~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\     +-------+ 
    {       Layer 3 IPv4, Ipv6 network             } === |Traffic|
    \~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~/     |Sniffer|
                192.168.1.*                              +-------+
                                                        192.168.1.1
\end{verbatim}   
}
\vspace{-0.5em}
\caption{Example of creating three ERSPAN monitoring sessions, $10, 20, 30$,
in a $10.1.1.*$ internal network, mirroring traffic over a $192.168.1.*$ IP network.}
\label{example}
\vspace{-1.0em}
\end{figure}

@@

# flow entry for port 2 to erspan tunnel 
ovs-dpctl add-flow \
    "in_port(2)" \
    "set(tunnel(tun_id=20,dst=192.168.1.1,ttl=64,\
    erspan(ver=2,dir=1,hwid=0x4),flags(df|key))),3"
\end{verbatim}

%\begin{lstlisting}
%[caption={Example ovs-dpctl usage},language=bash,label=lst:dpctl,breaklines=true]
%\end{lstlisting}

\subsection{iproute2 with/without eBPF}\label{iproute2}
Assuming we want to mirror all traffic from the physical device eth1
to an ERSPAN tunnel with session ID 30, as shown in the right Figure~\ref{example},
we first create a native-mode ERSPAN tunnel using ip-link command,
and mirror traffic from eth1 to the ERSPAN tunnel netdev.
For eBPF use case, instead of creating native-mode tunnel, we create
a metadata-mode tunnel using the key word "external".
Then, tc qdisc and filter rules are created for a eBPF program~\cite{daniel1,daniel2},
"test\_tunnel\_kern.o" with section name "set\_erspan" to be executed,
when receiving a packet from eth1 and sending through the "myerspan"
tunnel device.

%see net/ip6_gre_headroom.sh
\begin{verbatim}
# Native-mode without using eBPF
ip link add dev myerspan type erspan seq key 30 \
    local 192.168.1.4 remote 192.168.1.1 \
    erspan_ver 1 erspan 123
tc filter add dev eth1 ingress pref 1000 matchall \
    skip_hw action mirred egress mirror dev myerspan

# Metadata-mode with eBPF
ip link add dev myerspan type erspan external
tc qdisc add dev myerspan clsact
tc filter add dev myerspan egress bpf direct-action \
    obj test_tunnel_kern.o section erspan_set_tunnel
tc filter add dev eth1 ingress pref 1000 matchall \
    skip_hw action mirred egress mirror dev myerspan
\end{verbatim}

Note that for metadata-mode tunnel, the tunnel configuration is not
provided from the ip route command line, but is passed in to the tunnel
by the eBPF program, test\_tunnel\_kern.o. A code snippet creating this
object from tools/testing/selftests/bpf/test\_tunnel\_kern.c is shown below.
{\scriptsize
\begin{verbatim}
SEC("erspan_set_tunnel")
int _erspan_set_tunnel(struct __sk_buff *skb)
{
        struct bpf_tunnel_key key;
        struct erspan_metadata md; 
        int ret;

        __builtin_memset(&key, 0x0, sizeof(key));
        key.remote_ipv4 = 0xc0a80101; /* 192.168.1.100 */
        key.tunnel_id = 30; // session ID
        key.tunnel_tos = 0;
        key.tunnel_ttl = 64;

        ret = bpf_skb_set_tunnel_key(skb, &key, sizeof(key),
                                     BPF_F_ZERO_CSUM_TX);
        if (ret < 0) {
                ERROR(ret);
                return TC_ACT_SHOT;
        }

        __builtin_memset(&md, 0, sizeof(md));
        md.version = 1;
        md.u.index = bpf_htonl(123);

        ret = bpf_skb_set_tunnel_opt(skb, &md, sizeof(md));
        if (ret < 0) {
                ERROR(ret);
                return TC_ACT_SHOT;
        }

        return TC_ACT_OK;
}
\end{verbatim}
}
\section{Conclusion and Future Work}
\mycomment{
\section{Acknowledgments}
The authors would like to acknowledge Justin Pettit for his guidance on writing
this paper, Martynas Pumputis for providing context around WeaveNet, and Ben
Pfaff, Hannes Sowa and Yingying Ren for providing review feedback.
\section{Author Biography}
Joe Stringer is a software engineer interested in networks and related fields,
in particular SDN. He is actively engaged in the open-source community on
network software projects including Open vSwitch and the Linux networking
stack.
}
\bibliography{paper.bib}
\bibliographystyle{plain}
